---
output: github_document
---

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "##",
  error = TRUE,
  tidy = FALSE,
  fig.width = 8,
  fig.height = 8)
```

<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R build status](https://github.com/gaborcsardi/dotenv/workflows/R-CMD-check/badge.svg)](https://github.com/gaborcsardi/dotenv/actions)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/dotenv)](https://www.r-pkg.org/pkg/dotenv)
[![Coverage Status](https://img.shields.io/codecov/c/github/gaborcsardi/dotenv/master.svg)](https://codecov.io/github/gaborcsardi/dotenv?branch=master)
<!-- badges: end -->

# dotenv — Load environment variables from .env

This package loads the variables defined in the `.env` file
in the current working directory (as reported by `getwd()`),
and sets them as environment variables.

This happens automatically when the `dotenv` package is loaded,
so the typical use-case is to just put a `library(dotenv)` call at the
beginning of your R script.

Alternatively a `dotenv::load_dot_env()` call can be used
to load variables from arbitrary files.

## Installation

```{r eval = FALSE}
install.packages("dotenv")
```

## Usage

You can simply put

```{r eval = FALSE}
library(dotenv)
```

at the beginning of your script, to load the environment variables defined
in `.env` in the current working directory.

## File format

The `.env` file is parsed line by line, and line is expected
to have one of the following formats:

```
VARIABLE=value
VARIABLE2="quoted value"
VARIABLE3='another quoted variable'
# Comment line
export EXPORTED="exported variable"
export EXPORTED2=another
```

In more details:
 * A leading `export` is ignored, to keep the file
   compatible with Unix shells.
 * No whitespace is allowed right before or after the
   equal sign, again, to promote compatilibity with Unix shells.
 * No multi-line variables are supported currently. The
   file is strictly parsed line by line.
 * Unlike for Unix shells, unquoted values are _not_
   terminated by whitespace.
 * Comments start with `#`, without any leading
   whitespace. You cannot mix variable definitions and
   comments in the same line.
 * Empty lines (containing whitespace only) are ignored.

 It is suggested to keep the file in a form that is parsed the
 same way with `dotenv` and `bash` (or other shells).
